%-------------------------
% Resume in Latex
% Author : Baliram Shejal
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}


\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    {\Huge \scshape Baliram Shejal} \\ \vspace{1pt}
   Softwar Developer $|$ Pune,Maharashtra \\ \vspace{1pt}
    \small \href{tel:+919503838135}{ \raisebox{-0.1\height}\faPhone\ \underline{+91-9503838135} ~} \href{mailto:baliramshejal2001@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{baliramshejal2001@gmail.com}} ~ 
    \href{https://linkedin.com/in/balram01}{\raisebox{-0.2\height}\faLinkedinSquare\ \underline{Linkedin}}  ~
    \href{https://github.com/balram-01}{\raisebox{-0.2\height}\faGithub\ \underline{Github}} ~
    
    \vspace{-8pt}
\end{center}


%-----------PROFILE-----------
\section{PROFILE}
Experienced and dedicated Software Developer with 1 year and 6 months of expertise in mobile app development. Specialized in React JS, React Native, and the MERN stack. Proven track record leading projects in startup environments, demonstrating adaptability and a passion for creating seamless user experiences.

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vishwakarma Institute of Information And Technology, Pune }{JUN 2019 -- JUL 2023}
      {B.Tech. - Computer Engineering  - \textbf{CGPA} - \textbf{9.02}}{Pune, India}
  \resumeSubHeadingListEnd
  
%----%------RELEVANT COURSEWORK-------
\section{COURSEWORK / SKILLS}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-2pt, parsep=5pt]
                \item Mobile App Development: React Native, Android Studio, Android SDK
                \item Frontend Development: React JS, JavaScript, TypeScript
                \item Version Control: Git
                \item State Management: Redux
                \item MERN Stack Development
                \item API Development: REST API
                \item Programming Languages: Core Java
                \item Tools: VS Code
                \item Artificial Intelligence
                \item OOPS Concept
                \item Web Development
                \item Android Development
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd



%-----------EXPERIENCE-----------
\section{EXPERIENCE}
\resumeSubHeadingListStart

\resumeSubheading
  {\textbf{JustKolab}}{SEP 2022 -- PRESENT}
  {\underline{Mobile Application Developer}}{Pune, India}
  \resumeItemListStart
    \resumeItem{Led the evolution of JustKolab's mobile application from React.js to React Native.}
    \resumeItem{Served as the sole frontend developer, demonstrating versatility and mastery of React Native, clean code, and UI animations.}
    \resumeItem{Translated complex designs into user-friendly interfaces, significantly enhancing user satisfaction.}
    \resumeItem{Proven adaptability, showcased rapid learning, and committed to ongoing professional growth.}
  \resumeItemListEnd
\resumeSubheading
  {\textbf{Persistent}}{MAY 2022 -- JUN 2022} 
  {\underline{Intern}}{Pune, India}
  \resumeItemListStart
    \resumeItem{\normalsize{Interned at Persistent, mastering Java, Core Java, and OOPS.}}
    \resumeItem{\normalsize{Applied skills in real projects, enhancing code efficiency with Data Structures and Algorithms.}}
    \resumeItem{\normalsize{Gained valuable insights into the software development lifecycle.}}
  \resumeItemListEnd 

\resumeSubHeadingListEnd
\vspace{-12pt}

%-----------PROJECTS-----------
\section{Academic Project}
    \vspace{-5pt}
    \resumeSubHeadingListStart
       \resumeProjectHeading
          {\href{https://github.com/balram-01/Industry-project}{\textbf{\large{\underline{NLP E-Commerce Chatbot}}} \href{https://github.com/balram-01/Industry-project}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{Python,
NLTK ,
TensorFlow,
Pickle
}}}{AUG 2022 – SEPT 2022}
          \resumeItemListStart
            \resumeItem{\normalsize{\textbf{Aim :} Develop dynamic Python chatbot with NLP for engaging E-Commerce assistance on WhatsApp.}}

             \resumeItem{\normalsize{\textbf{Technical Contribution :} Integrated NLTK, TensorFlow for intelligent interactions.		
Crafted personalized responses for enhanced user engagement. 
Optimized model management using pickle for efficiency.
Created interactive product showcase, facilitating seamless transitions. 
}}
          \resumeItemListEnd 
 
          
    \resumeSubHeadingListEnd
\vspace{-12pt}

%

% -----------PROJECTS-----------
\section{Freelance Project}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\large{\underline{E-Commerce Mobile App}} \small{$|$ \underline{React native, Node.js, Express.js, MongoDB, JWT}}}}{OCT 2023 – DEC 2023}
\resumeItemListStart
\resumeItem{\normalsize{\textbf{Aim:} Create a robust E-Commerce mobile app mimicking Amazon, focusing on seamless user experience.}}
\resumeItem{\normalsize{\textbf{Technical Contribution:} Developed RESTful API with Node.js, Express.js, MongoDB for user registration, email verification, and address management. Ensured secure authentication using JSON Web Tokens, proficient error handling, and a responsive interface, showcasing diverse technology integration.}}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{\large{\underline{Social Media App Backend}} \small{$|$ \underline{Express.js, Node js, Mongodb, }}}}{DEC 2023 – JAN 2023}
\resumeItemListStart
\resumeItem{\normalsize{\textbf{Aim:} Develop a dynamic backend for a social media app with user CRUD, post operations, and secure authentication.}}
\resumeItem{\normalsize{\textbf{Technical Contribution:} Developed Express.js APIs for user management. Implemented APIs for post CRUD operations. Ensured secure authentication mechanisms. Focused on scalability and performance optimization.}}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{\large{\underline{ESports Tournament App}} \small{$|$ \underline{React Native, MERN stack}}}}{JAN 2024 – PRESENT}
\resumeItemListStart
\resumeItem{\normalsize{\textbf{Aim:} Develop an eSports tournament app using MERN stack for seamless and engaging tournament management.}}
\resumeItem{\normalsize{\textbf{Technical Contribution:} Leveraging React Native for cross-platform compatibility. Integrating MERN stack for robust backend and frontend development. Designing intuitive user interfaces for efficient tournament management. Implementing real-time updates for a dynamic user experience.}}
\resumeItemListEnd

\resumeSubHeadingListEnd



%-----------PROGRAMMING SKILLS-----------
\section{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small
    \item \textbf{Languages:} JavaScript, TypeScript, Java
    \item \textbf{Developer Tools:} VS Code, Android Studio, Postman
    \item \textbf{Technologies/Frameworks:} GitHub, ReactJS, Redux,  NodeJS, ExpressJS, Git, Mongo, React Native
    \item \textbf{Mobile App Development:} React Native, Android Studio, Android SDK
    \item \textbf{Version Control:} Git
    \item \textbf{MERN Stack Development:} MongoDB, ExpressJS, ReactJS, NodeJS (Intermediate)
    \item \textbf{API Development:} REST API
    \item \textbf{Other:} Core Java, JSON
\end{itemize}
\vspace{-15pt}



%-----------CERTIFICATIONS---------------
\section{CERTIFICATIONS}
\hspace{9.5pt}
$\sbullet[.75] \hspace{0.1cm}$ {\href{https://www.linkedin.com/posts/balram01_android-developer-bootcamp-activity-6951899844311420929-x4Bf?utm_source=share&utm_medium=member_desktop}{The Comprehensive Android Developer Bootcamp\, \faExternalLink}} \hspace{1cm}
$\sbullet[.75] \hspace{0.1cm}$ {\href{https://www.linkedin.com/posts/balram01_internship-persistent-activity-6965962357395116033-fEmY?utm_source=share&utm_medium=member_desktop}{Martian Internship Program\, \faExternalLink}}

%-----------INVOLVEMENT---------------
\section{EXTRACURRICULAR}
    \resumeSubHeadingListStart
        \resumeSubheading{NLP-Powered E-Commerce Assistant Copyright}{ DEC 2023}{\underline{Published Copyright}}{Pune, India}
            \resumeItemListStart
                \resumeItem{\normalsize{Published Copyright for NLP-Powered E-Commerce Assistant, showcasing NLP and e-commerce expertise.}}
                \resumeItem{\normalsize{Participation Certificate.}}
            \resumeItemListEnd
        
        \resumeSubheading{YouTube Gaming Video Copyright}{ DEC 2023}{\underline{Copyrighted Video}}{Pune, India}
            \resumeItemListStart
                \resumeItem{\normalsize{Copyrighted YouTube gaming video with 1M+ views demonstrating content creation skills.}}
                \resumeItem{\normalsize{Participation Certificate.}}
            \resumeItemListEnd
        
        \resumeSubheading{NLP Project Leadership}{ NOV 2023}{\underline{Team Leader}}{Pune, India}
            \resumeItemListStart
                \resumeItem{\normalsize{Led a team of 4 for NLP project, highlighting leadership.}}
                \resumeItem{\normalsize{Participation Certificate.}}
            \resumeItemListEnd
        
        \resumeSubheading{YouTube Channel Achievements}{DEC 2023}{\underline{Achievements}}{Pune, India}
            \resumeItemListStart
                \resumeItem{\normalsize{Gained 37k+ YouTube subscribers showcasing academic and online community achievements.}}
                \resumeItem{\normalsize{Participation Certificate.}}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-11pt}


 
\end{document}
